---
title: "R_607_Week_7a_Hmk_HTML_XML_JSON__Daniel_Thonn"
output: html_document
course: R-607 CUNY MSDA program

---

## Assignment 607_Homework-7: Hmw_607_Working_with_XML_and_JSON_in_R_Daniel_Thonn

Summary of Assignment
This assignment involves loading and Transforming HTML,XML, and JSON data

This Assignment requires the following:

1). R-Studio

The following R-packages are used:
#install.packages("XML")
#install.packages("RCurl")
#install.packages("RJSONIO")


Steps to reproduce:
1). Place the following (3) files in directory: "C:\mysqldata"
books_dt.html
books_dt.xml
books_dt.JSON

2). run the R-Studio file: R_607_Week_7a_Hmk_HTML_XML_JSON__Daniel_Thonn.Rmd


Setting up and Preparing the Environment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}

#install.packages("XML")
library(XML)
#install.packages("RCurl")
library(RCurl)
#install.packages("RJSONIO")
library(RJSONIO)

```


Load the HTML file and check structure


```{r, echo=TRUE}
# Load the HTML file
html_1 <- getURL("https://raw.githubusercontent.com/danthonn/607_Week_7/master/books_dt.html")
html_1

# Read into an HTML table
html_2 <- readHTMLTable(html_1, header=TRUE)
html_2

# Read into a Data Frame and check output
html_3 <- as.data.frame(html_2)
html_3
head(html_3)

```



Load the XML file and check structure

```{r, echo=TRUE}
# Load the XML file
xml_1 <- getURL("https://raw.githubusercontent.com/danthonn/607_Week_7/master/books_dt.xml")
xml_1
# Parse the XML file
xml_2 <- xmlTreeParse(xml_1)

# Display the XML file
root_1 <- xmlRoot(xml_2)
xml_3 <- xmlSApply(root_1, xmlValue)
xml_3

# Load the XML file into a Data Frame
xml_4 <- as.data.frame(xml_3)
xml_4


```


Load the JSON file and check structure

```{r, echo=TRUE}
# Load the JSON file
json_1 <- getURL("https://raw.githubusercontent.com/danthonn/607_Week_7/master/books_dt.JSON")
json_1

# Read raw data into improved format
json_2 = RJSONIO::fromJSON(json_1)
json_2

# Place in a data frame
json_3 <- as.data.frame(json_2)
json_3


```


Conclusion: The outputs of HTML, XML, and JSON are different, though similar once loaded to a data frame. They contain the same information in different formats.   For further processing these different formats would need to be handled differently to extract and process the same information contained within.



#END
